Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-04-09 analysis/paper/paper.Rmd
makeTests function rewrite to use 'grouping' var

@@

But in the ANAscore variable it shows up to be significant ! Yellowjackets stings are more severe than the bee stings. This is however very hard to compare to refractory cases. Maybe we can use the refractory case identifier to say in which group we see more refractory cases?

>>>>

### Adrenaline use is lower in patients with IVA compared to other anaphylaxis cases

```{r}
grid.draw(fig_adrenuse1)
```

I matched patients with IVA to a group of similarly severe cases of non-IVA anaphylaxis and evaluated the use of Adrenaline in both of these groups.

@@

But in the ANAscore variable it shows up to be significant ! Yellow-jackets stings are more severe than the bee stings. This is however very hard to compare to refractory cases. Maybe we can use the refractory case identifier to say in which group we see more refractory cases?
